working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits authors and affiliations

---
title: working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect
author:
- affilnum: '1,2,3'
  name: Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
  email: barragansljose@gmail.com
affiliation:
- affil: University of New England (Australia)
  affilnum: 1
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 2
- affil: Department of Biological Sciences, University of Pittsburgh 4249 Fifth Avenue, Pittsburgh, Pennsylvania 15260-3929 USA
  affilnum: 3
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  word_document: null
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

>>>>

---
title: working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect
author:
- name: Jose B. Lanuza
  affilnum: 1
  email: barragansljose@gmail.com

- name: Ignasi Bartomeus
  affilnum: 2

- name: Tia-Lynn Ashman  
  affilnum: 3

- name: Romina Rader
  affilnum: 1

affiliation:
- affil: University of New England (Australia)
  affilnum: 1
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 2
- affil: Department of Biological Sciences, University of Pittsburgh 4249 Fifth Avenue, Pittsburgh, Pennsylvania 15260-3929 USA
  affilnum: 3
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  word_document: null
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits authors and affiliations

\title{working title Compatibility system and stigma size are the main
predictors of heterospecific pollen effect}
\author{
Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge working title Compatibility system and stigma size are the main
predictors of heterospecific pollen effect
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader \textsuperscript{*} \textsuperscript{1,2,3} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}University of New England (Australia)\\*
\\*
\textsuperscript{2}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
\\*
\textsuperscript{3}Department of Biological Sciences, University of Pittsburgh 4249 Fifth
Avenue, Pittsburgh, Pennsylvania 15260-3929 USA\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

>>>>

\title{working title Compatibility system and stigma size are the main
predictors of heterospecific pollen effect}
\author{
Jose B. Lanuza
Ignasi Bartomeus
Tia-Lynn Ashman
Romina Rader
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge working title Compatibility system and stigma size are the main
predictors of heterospecific pollen effect
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza \textsuperscript{*} \textsuperscript{1} 
Ignasi Bartomeus \textsuperscript{2} 
Tia-Lynn Ashman \textsuperscript{3} 
Romina Rader \textsuperscript{1} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}University of New England (Australia)\\*
\\*
\textsuperscript{2}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
\\*
\textsuperscript{3}Department of Biological Sciences, University of Pittsburgh 4249 Fifth
Avenue, Pittsburgh, Pennsylvania 15260-3929 USA\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize
